---
title: "Sample Sow"
output: word_document
date: "2023-09-27"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE, include=FALSE}

package_loader <- function(x) {
  if (x %in% installed.packages()) {
    library(x, character.only = TRUE)
  } else {
    install.packages(x)
    library(x, character.only = TRUE)
  }
}

lapply(c("tidyverse", "googlesheets4"), package_loader)
```

Pulling the information from google sheets
```{r, echo=FALSE, include=FALSE}
# authenticate google sheets
# gs4_auth()

# get sheet data and turn it into a df
sheet_url <- "https://docs.google.com/spreadsheets/d/1miAXjWnqgDg3wbi3Rp3NESF2fs7kTE7mQZNEP6qiOMA/edit#gid=2092154335"
my_sheet <- gs4_get(sheet_url)
sheet_data <- read_sheet(my_sheet)
```

Timestamp: `r sheet_data[1,1]`

First name: `r sheet_data[1,2]`

Last name: `r sheet_data[1,3]` 

Org: `r sheet_data[1,3]`  

Email: `r sheet_data[1,5]`  

Funding: `r sheet_data[1,6]`  

Project Name: `r sheet_data[1,7]`  

Project description: `r sheet_data[1,8]`  

Tasks: `r sheet_data[1,9]`  

Deliverables: `r sheet_data[1,10]`  

Time frame: `r sheet_data[1,11]`  

Comments: `r sheet_data[1,12]`  

Amount of funding: `r sheet_data[1,13]`  

Contract required: `r sheet_data[1,14]`  

Phone number: `r sheet_data[1,15]`  
